Deep mutational scanning of hemagglutinin helps distinguish the evolutionary fates of human H3N2 influenza virus lineages

### 2018-01-23 paper/manuscript.tex
one tiny edit

\begin{suppfigure}
\centerline{\includegraphics[width=0.75\textwidth]{figs/S04_post_Perth2009/post_Perth2009_seqpref.pdf}}
\caption{\label{suppfig:future}
{\bf The sequence preference of nodes that occur after the split of Perth/2009 off the trunk.}
Our experiments show a selective advantage for the trunk even if we limit the analysis to sequences that occur after the split of Perth/2009 off the trunk.
(A) Phylogenetic tree showing all nodes that branch from the trunk before or contemporaneously with Perth/2009 (orange), all nodes that occur after the branch to Perth/2009 for which we can resolve the trunk (red) or side branches (blue), and all nodes for which it is not yet clear which sequences will be on the trunk or side branches.
In this figure, we restrict the analysis to the nodes in red and blue.
(B)  
Average per-site sequence preference (similar to Figure~\ref{fig:trunkvssidebranch}C) for all trunk and side-branch nodes that occur after the branch to Perth/2009.
(C)
The sequence preferences of nodes on the trunk generally exceed those of nodes on the side branches along the post-Perth/2009 portion of the tree.
Note that because there are relatively few post-Perth/2009 sequences for which we can currently distinguish trunk from side branch, the number of points in this plot is small, precluding meaningful statistical analyses of the type performed in Figure~\ref{fig:trunkvssidebranch}B.
}
\end{suppfigure}

>>>>

\begin{suppfigure}
\centerline{\includegraphics[width=0.75\textwidth]{figs/S04_post_Perth2009/post_Perth2009_seqpref.pdf}}
\caption{\label{suppfig:future}
{\bf The sequence preference of nodes that occur after the split of Perth/2009 off the trunk.}
Our experiments show a selective advantage for the trunk even if we limit the analysis to sequences that occur after the split of Perth/2009 off the trunk.
(A) Phylogenetic tree showing all nodes that branch from the trunk before or contemporaneously with Perth/2009 (orange), all nodes that occur after the branch to Perth/2009 for which we can resolve the trunk (red) or side branches (blue), and all nodes for which it is not yet clear which sequences will be on the trunk or side branches (gray).
In this figure, we restrict the analysis to the nodes in red and blue.
(B)  
Average per-site sequence preference (similar to Figure~\ref{fig:trunkvssidebranch}C) for all trunk and side-branch nodes that occur after the branch to Perth/2009.
(C)
The sequence preferences of nodes on the trunk generally exceed those of nodes on the side branches along the post-Perth/2009 portion of the tree.
Note that because there are relatively few post-Perth/2009 sequences for which we can currently distinguish trunk from side branch, the number of points in this plot is small, precluding meaningful statistical analyses of the type performed in Figure~\ref{fig:trunkvssidebranch}B.
}
\end{suppfigure}
